\documentclass[]{letter}
\usepackage{fullpage}
\usepackage{xcolor}
\usepackage{hyperref}

\colorlet{urlcolor}{blue!40!black}

\hypersetup{colorlinks=true,
	urlcolor=urlcolor}

\begin{document}
\begin{letter}{The University of Vermont \\ Burlington, VT 05405}
%\address{Anthony J. Barrows \\ 38 Crombie St. Apt. 2 \\ Burlington, VT 05401}
	
	\begin{center}
		\textbf{\Huge \scshape Anthony J. Barrows} \\ \vspace{3pt}
		\small 38 Crombie St. Apt. 2, Burlington, VT 05401 $|$
		\small (802) 839-8115 $|$
		\href{mailto:ajbarrow@uvm.edu}{anthony.barrows@uvm.edu}
	\end{center}
\opening{To Whom it May Concern,}
It is with enthusiasm that I express my interest for the TCORS Research Analyst position. I have held multiple tobacco regulatory science positions at the Vermont Center on Behavior and Health (VCBH), fulfilling different roles as organizational needs arise. With guidance from mentors, a graduate education, and commitment to perpetual improvement and innovation, I am confident that I can continue to be a valuable resource to the center.

I graduated with honors and accolades from the University of Hartford where, in addition to learning the fundamentals of behavioral science, I developed my ability to express complete ideas clearly. I strongly believe that clear writing represents clear thinking, a principle that lends to the careful pursuit of medical research. As a Research Assistant, this principle manifested in attention to detail, and sensitivity to participants with serious psychiatric conditions like depression, anxiety, and substance use disorders. As Lead Research Assistant, my colleagues saw clean guidance toward protocol adherence, solutions to complicated problems, and respect for a diversity of opinions and perspectives.

Most recently, as I complete a Master's in Complex Systems and Data Science at UVM, I have led many of the center's technical operations, including database development, and research data analysis using advanced scripting and visualization techniques to emphasize clear, reproducible results. In particular, I constructed a fully-automated data dashboard which provides interactive visualization and summary analysis of real-time clinical trial metrics, eliminating manual preparation while also expanding accuracy, precision, and detail. Taking the post-disciplinary approach taught in complex systems provides a more complete understanding of the ways in which research data analysis helps write narratives about underlying mechanisms, inviting generalized conclusions and more informed questions. This story-telling model defines my work, from developing data structures to preparing in-lab reports and publishable manuscripts.

The intersection of technical skills honed through experience and a graduate education and the clear-thinking approach developed through nearly five years in tobacco regulatory science at UVM makes me an excellent candidate to help VCBH continue producing exceptional work. I look forward to discussing my qualifications in more detail, including my commitment to pursuing advanced research ends at a top-tier university. Thank you for your time and consideration.


\signature{Anthony J. Barrows}

\closing{Sincerely,}

%enclosure listing
\encl{R\'esum\'e}

\end{letter}
\end{document}
