%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{etaremune}
\usepackage{bibentry}
\usepackage{graphicx}
\usepackage{hyperref}
\input{glyphtounicode}




%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% AJB additioins
\colorlet{urlcolor}{blue!40!black}

\hypersetup{colorlinks=true,
	urlcolor=urlcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Anthony J. Barrows} \\ \vspace{3pt}
    \small (802) 839-8115 $|$ \href{mailto:ajbarrow@uvm.edu}{anthony.barrows@uvm.edu} $|$ 
    \href{https://linkedin.com/in/ajbarrows}{\textbf{linkedin}.com/in/ajbarrows} $|$ \href{https://github.com/ajbarrows}{\textbf{github}.com/ajbarrows}
%    \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://uvm.edu}{\textbf{The University of Vermont}}}{Burlington, VT}
      {\href{https://vermontcomplexsystems.org/}{M.S. in Complex Systems and Data Science}}
      {Aug. 2019-- May 2021}
    \resumeSubheading
      {\href{https://www.hartford.edu/}{\textbf{University of Hartford}}}{Hartford, CT}
      {\href{https://www.hartford.edu/academics/schools-colleges/arts-sciences/academics/departments-and-centers/psychology/default.aspx}{B.A. in Psychology;} \href{https://www.hartford.edu/academics/schools-colleges/arts-sciences/academics/departments-and-centers/sociology-and-criminal-justice/default.aspx}{Minor in Criminal Justice}}
      {Aug. 2013 -- May 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
	\resumeSubheading{\href{http://www.med.uvm.edu/behaviorandhealth/home}{Vermont Center on Behavior and Health}}
	{Burlington, VT}{Research Data Analyst}{June 2021 -- Present}
	     \resumeItemListStart
	        \resumeItem{Independently developed automated clinical trial dashboards that eliminated time-consuming manual reports.}
	        \resumeItem{Engineered data cleaning and transformation pipelines making trial data available for immediate use, reducing analysis delays. }
	        \resumeItem{Design and administer electronic data capture (REDCap) projects for several research projects.}
	        \resumeItem{Produce analytical reports using open-source code making results transparent, reproducible, and accessible. }
	        \resumeItem{Design, program, and maintain secure databases for research data and PII.}
	        \resumeItem{Identify inefficiencies and implement solutions using automation to improve data collection methods.}
	        \resumeItem{Collaborate with statisticians to manage and analyze data for publication, focusing on quality tables and figures.}
			\resumeItem{Review study data to ensure compliance with research protocols, training staff on best practices.}
%	        \resumeItem{Coordinate with outside vendors to oversee the design and maintenance of digital data collection systems.}
	        \resumeItem{Prepare time-sensitive reports for regulatory boards and funding agencies.}
		\resumeItemListEnd
	\resumeSubSubheading{Research Assistant (Promoted to Team Lead October 2018)}{October 2016 -- June 2021}
		\resumeItemListStart
			\resumeItem{Implemented NIDA/FDA grant-funded study on long term exposure to low nicotine cigarettes (e.g., physiological and psychological testing, distributing study product).}
			\resumeItem{Supervised participant recruitment, and implemented procedures to improve response and retention.}
			\resumeItem{Coordinated with study principal investigators to assess clinical challenges and quickly find effective solutions.}
			\resumeItem{Trained research staff to conduct participant sessions and use specialized laboratory equipment.} 
		\resumeItemListEnd
	\resumeSubheading{\href{https://www.orcamedia.net}{ORCA Media}}
		{Montpelier, VT}{Videographer and Video Editor}{January 2009 -- September 2016}
		\resumeItemListStart
		\resumeItem{Filmed and edited local media events to broadcast specifications, focusing on immediate turnaround.}
		\resumeItem{Developed a lifelong love for non-profit news media.}
		\resumeItemListEnd
		

%    \resumeSubheading
%      {Lead Research Assistant}{October 2018 -- Present}
%      {\href{http://www.med.uvm.edu/behaviorandhealth/home}{Vermont Center on Behavior and Health}}
%      {Burlington, VT}
%      \resumeItemListStart
%        \resumeItem{Develop and maintain interactive clinical trial reporting tools for investigator use.}
%        \resumeItem{Design, program, and maintain secure databases for storing sensitive information.}
%        \resumeItem{Collaborate with statisticians to manage and analyze data for presentations and publications.}
%        \resumeItem{Develop analytical reports using tools like R Markdown with a focus on reproducible results.}
%		\resumeItem{Review study data to ensure compliance with research protocols.}
%        \resumeItem{Coordinate with outside vendors to oversee the design and maintenance of digital data collection systems}
%        \resumeItem{Maintain clinical trial's participant-facing web page using Apache web server.}
%      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%     \resumeItemListEnd
%-------------------------------------------

%    \resumeSubheading
%      {Research Assistant}{Oct. 2016 -- Oct. 2018}
%      {\href{http://www.med.uvm.edu/behaviorandhealth/home}{Vermont Center on Behavior and Health}}{Burlington, VT}
%      \resumeItemListStart
%        \resumeItem{Implement NIDA/FDA grant-funded study on long term exposure to low nicotine cigarettes.}
%        \resumeItem{Independently coordinate physiological and psychological testing (e.g., breath and urine analysis, psychiatric inventory), distributing study product, compensating participants, and ensuring adherence to IRB, DSMB and NIH-NIDA guidelines.}
%        \resumeItem{Train research staff to conduct participant sessions and use specialized equipment.}
%    \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Example Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Enrollment Reports} $|$ \emph{R, R Shiny, Plotly, REDCap API, Linux CLI}}{\textit{\small January 2020 -- Present}}
          \resumeItemListStart
            \resumeItem{Create and maintain interactive data dashboards for instantaneous and longitudinal reporting.}
            \resumeItem{Interface with multiple APIs and fundamentally different data sources to retrieve information.}
            \resumeItem{Employ principles of tidy data management to create an efficient aggregation pipeline.}
            \resumeItem{Build filtering tools to allow for flexible, live data exploration, prompting new insight from advanced visualizations, summaries, and rapid analyses.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			\textbf{Languages}{: R, Python, \LaTeX, Markdown} \\
			\textbf{Visualization Tools}{: R Shiny, ggplot2, Plotly} \\
			\textbf{Frameworks}{: SQL, Microsoft Access, Linux CLI, REDCap API, Google Analytics} \\
			\textbf{Developer Tools}{: R Studio, R Markdown,  Jupyter, VS Code} \\
			\textbf{Version Control}{: Git, GitHub} \\
			\textbf{Libraries}{: tidyverse, randomLCA, pandas, NumPy, Matplotlib, scikit-learn} \\
			\textbf{Software}{: Microsoft Excel, REDCap (Project Design), Final Cut Pro}
	}}
\end{itemize}

% ----------AFFILIATIONS------------------
\section{Affiliations}
	\resumeSubHeadingListStart
		\resumeSubheading{\href{https://www.jazzinthemountains.com/}{BDI Enterprises, LLC}
		}
		{East Montpelier, VT}
		{Founder, Limited Partner}{Oct. 2020 -- Present}
		\resumeItemListStart
		    \resumeItem{Organize educational jazz summer camps for adult musicians.}
		    \resumeItem{Maintain business website, produce promotional videos and recordings.}
		\resumeItemListEnd
	\resumeSubHeadingListEnd
	

%


\end{document}
